Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-29 manuscript.Rmd
Edits to nonlinear methods section

## Use of Nonlinear Methods in Naturally Occurring Data
Traditional linear analyses have led to many notable discoveries in the
domains of psychology and political science, but continuous data pose
problems that are not easily overcome with these methods. Events have
historically been conceptualized as linear chains of smaller, sequential
events with one occurrence leading to the next. This notion has been
increasingly replaced by ideas from dynamical systems theory. Rather than
a chain of events, continuous data can be thought of as nested occurrences,
where mutually constrained parts (e.g., citizens, governments, real-world
events, social media platforms) are constantly interacting, leading to
more global behaviors that are larger than the sum of the parts
[@turvey2018lectures]. When analyzed as dynamical systems, many phenomena
exhibit new nonlinear patterns that were formerly overlooked. Continuous
data subject to linear analyses becomes flattened, and the variability
that is fundamental to these systems and their evolution over time is
ignored. Nonlinear methods provide means for capturing the rich temporal
dynamics and variability that unfold in continuous data.

The primary methods used in the current work is cross-recurrence
quantification analysis [CRQA; @zbilut1998detecting] and its offshoot,
windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence].
CRQA has successfully been used to gain a better understanding of many
complex human phenomena, such as human social interactions
[for a review, see @fusaroli2014analyzing] and interpersonal synchrony
[@paxton2017interpersonal]. We argue that the use of nonlinear methods in
the investigation of political science phenomena will lead to new insights
and development of more robust theories.

>>>>

## Using Nonlinear Methods to Capture Complex Relationships
Given the hypothesized interrelationship between the real-world
and online actions---and the notorious messiness of naturally occurring
data---it is critical to find appropriate analysis tools that can
identify the complex interconnections.
Traditional linear analyses have led to many notable discoveries in the
domains of psychology and political science, but time series data pose
problems that are not easily overcome with these methods. Events have
historically been conceptualized as linear chains of smaller, sequential
events with one occurrence leading to the next. 
Certain kinds of data are relatively well-suited to these analyses,
but messy, complex, variable data from real-world events can pose
challenges from overpowered samples to violation of underlying
statistical assumptions [@paxton2017finding].

At the same time, the foundational theoretical assumptions of a 
linear world has been
increasingly replaced by ideas from dynamical systems theory. Rather than
a chain of events, time series data can be thought of as nested occurrences,
where mutually constrained parts (e.g., citizens, governments, real-world
events, social media platforms) are constantly interacting, leading to
more global behaviors that are larger than the sum of the parts
[@turvey2018lectures]. Linear analyses flatten these nonlinear patterns in 
time series data and ignore the variability
that is fundamental to these systems and their evolution over time. 
However, when analyzed as dynamical systems, many phenomena
exhibit new nonlinear patterns that were formerly overlooked. 
Nonlinear methods provide means for capturing the rich temporal
dynamics and variability that unfold in time series data.

Although a number of other nonlinear methods exist, 
the primary nonlinear method used in the current work is cross-recurrence
quantification analysis [CRQA; @zbilut1998detecting] and its offshoot,
windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence].
CRQA has successfully been used to gain a better understanding of many
complex human phenomena, including a variety of human social interactions
[for a review, see @fusaroli2014analyzing]. 
Much as it has for psychology, we argue that the use of nonlinear methods in
the investigation of political science phenomena will lead to new insights
and the development of more robust theories.
